Citeopotamus

### 2012-12-08 paper/paper.tex
Committing minor changes

\begin{figure*}[ht]
   \includegraphics[width=\textwidth px]{images/arch.eps}
        \caption{The Citeopotamus architecture overlaid on a hippopotamus.}
        \label{fig:arch}
\end{figure*}

@@

\subsubsection{Structure of Paper Text}
%TODO(aldrin): Expand here if necessary
If the paper text was generated from OCR, then the structure of the text was left up to the OCR engine.
However, papers scraped from PLOS were in HTML and extra formatting can be inferred.

@@

\subsection{Structured Paper Directory Format}\label{sec:paperFormat}
The output of the scraper is a directory that contains information about the root paper and all the reference that were collected.
To make all the information easily accessible to anyone without imposing any arbitrary restrictions, the structure of the
data is enforced by directory structure.

@@

Every directory that represents a paper will have at most four files:
\begin{enumerate}
   \item meta.txt -- Contains the title, authors, tags, categories, and abstract. This is the only file required for every paper directory.
   \item paper.pdf -- The pdf version of the paper.
   \item paper.txt -- The text version of the paper. This file is required for the root paper.
   \item refs.txt -- Only the references that appear at the bottom of the paper. This information is duplicated in paper.txt, but placed here for convenience.
\end{enumerate}

@@

\begin{figure}[ht]
   \includegraphics[width=\columnwidth px]{images/tree.eps}
        \caption{The structure of a paper directory.}
        \label{fig:tree}
\end{figure}

@@

We will use the following actual sentence as a running example:
\begin{quote}
In previous work, the Guyton models were modularized and re-implemented in Fortran, C++ (M2SL \textbf{[]}), and Simulink \textbf{[]}.
\end{quote}

@@

\subsubsection{Parsing and Scraping}
Parsing is vital to the Citeopotamus system. If a context is improperly parsed, then everything else around that citation falls apart.
A spot check of papers that perform poorly (under 10\% accuracy) reveals that many of these these papers have many incorrectly parsed contexts.
Some of these errors come from an error in parsing like missing a false positive sentence ender. However, most of these errors appear to
come from difficulties scraping the paper. We believe that irregularities in the paper's HTML causes poor formatting of the resulting
plain text paper and therefore causes parsing errors.

>>>>

\begin{figure*}[ht]
   \includegraphics[width=\textwidth]{images/arch.eps}
        \caption{The Citeopotamus architecture overlaid on a hippopotamus.}
        \label{fig:arch}
\end{figure*}

@@

\subsubsection{Structure of Paper Text}\label{sec:text_structure}
If the paper text was generated from OCR, then the structure of the text was
left up to the OCR engine.  However, papers scraped from PLOS were in HTML and
extra formatting can be inferred.

@@

\subsection{Structured Paper Directory Format}\label{sec:dir_structure}
The output of the scraper is a directory that contains information about the
root paper and all the reference that were collected.  To make all the
information easily accessible to anyone without imposing any arbitrary
restrictions, the structure of the data is enforced by directory structure.

@@

Every directory that represents a paper will have at most four files:
\begin{description}
   \item[meta.txt\footnotemark{1}] Contains the title, authors, tags, categories, and abstract.
                   This is the only file required for every paper directory.
   \item[paper.txt\footnotemark{1}] The text version of the paper. This file is required for
                    the root paper.
   \item[refs.txt\footnotemark{1}] Only the references that appear at the bottom of the paper.
                   This information is duplicated in paper.txt, but placed here
                   for convenience.
   \item[paper.pdf] The pdf version of the paper.
   \item[paper.html] The HTML version of the paper. This is grabbed should
                     the paper need to be re-parsed.
\end{description}

\footnotetext[1]{These files are not required for our implementation to work}

@@

\begin{figure}[ht]
   \includegraphics[width=\columnwidth]{images/tree.eps}
        \caption{The structure of a paper directory.}
        \label{fig:tree}
\end{figure}

@@

We will use the following actual sentence as a running example:
\begin{quote}
In previous work, the Guyton models were modularized and reimplemented in Fortran, C++ (M2SL \textbf{[]}), and Simulink \textbf{[]}.
\end{quote}

@@

\subsubsection{Parsing and Scraping}
Parsing is essential to the Citeopotamus system. If a context is improperly parsed, then everything else around that citation falls apart.
A spot check of papers that perform poorly (under 10\% accuracy) reveals that many of these these papers have many incorrectly parsed contexts.
Some of these errors come from an error in parsing like missing a false positive sentence ender. However, most of these errors appear to
come from difficulties scraping the paper. We believe that irregularities in the paper's HTML causes poor formatting of the resulting
plain text paper and therefore causes parsing errors.
